Tor's Usability for Censorship Circumvention

### 2016-04-05 pets2017-paper/pets2017-paper.tex
Explain DNFs in the figure caption.
formatting tweaks, intros, and todos

\subsection{Methodology} 
\subsubsection{Setup}
\label{sec:setup}
We simulated three censorship environments for our experiment.
These reproducible, stable environments are informed by our experience 
with pluggable transports and knowledge of commonly seen censorship 
techniques. Their goal in our user study is not to replicate the network 
environment in any particular country, but to require our participants to 
configure Tor Browser in distinct configurations.

@@

\subsubsection{Results} 
In this section, we discuss problems encountered by our participants at each step of the configuration process and solutions to those problems. We conclude with our goals for improving the configuration interface. Because of the small sample size of qualitative studies, we can only state that these are problems that participants can encounter when configuring. We confirm the statistical significance of some of the problems in our quantitative study (section ~\ref {sec:quantitative}. All quotes are paraphrased from live transcriptions of participant interviews.\\

\noindent {\bfseries Connect vs. Configure} 
The first task for our participants was to decide between connecting directly to the Tor network or configuring their connection. Text in the interface tells people that connecting directly ``will work in most situations'' and instructs to configure a bridge or proxy if the ``Internet connection is censored or proxied.'' We found that a majority of our participants did not take the time to read the text on the screen and that if they did, the text did not always soundly influence their decision.

@@

\noindent {\bfseries Bridge Configuration} 
When a participant chooses to configure their connection, their next step is to determine whether they need to configure a bridge, and to configure one if necessary. Answering yes to ``Does your Internet Service Provider (ISP) block of otherwise censor connections to the Tor Network'' directs to a bridge configuration screen, whereas answering no skips that screen. We observed that multiple participants struggled with the technical language on the screen, and ultimately decided to try trial and error. Most participants with the default option to not configure a bridge.

@@

\noindent {\bfseries Proxy Configuration} 
After the bridge configuration, the participant again is asked to answer a question to determine if they need a proxy and if so, to configure one. This question also was too technical for some participants.

@@

\noindent{\bfseries Progress Bar} 
Users were generally displeased with the lack of feedback on the progress bar. The process seemed to take too long for them, even in the ideal case in which a user chose the correct configuration in the first attempt. If users chose particular wrong configurations (i.e. a syntactically valid but nonfunctional proxy), they would be waiting for an indefinite period of time, because there is no timeout.

@@

\noindent{\bfseries User Communication Failure} Many participants, including participants who were pre-screened for high technical ability and previous experience with using Tor, were not familiar with the vocabulary. 
\begin{quotation}
\noindent P2:\textit{"I don't know what any of those means (list of bridges),or what that (proxy)
 means at all."}\\

@@

\noindent{\bfseries Final Thoughts}
We believe that the interface is too technical for users to understand and overburdens users with tasks. From our observations in this qualitative study, our goal in redesigning the interface was to making the vocabulary more accessible to the average user, requiring the user to make fewer decisions, and automating parts of configuration that don't increase risk to high-risk users.

@@

\section{Redesigning the Configuration Interface}

@@

Changes made: 
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt 
\item Made first screen more clear to help users decide on connect vs configure. 
\item Got rid of question screens. 
\item Put the proxy first. It makes sense topologically. 
\item Added auto-detect for proxies. 
\item Gave explicit advice on how to choose bridges. 
\item Added a summary screen. 
\item Added a topological progress bar that works every time. 
\item Gives instructions on what to try next after failure. 
\item Greatly reduced text and made text easier to read. 
\item Less visual clutter for users. Hide things until user clicks on them. 
\end{itemize}

Talk about how the design as a conservative design. And why the conservative choices were made. For at-risk users, maintainability, etc.

@@

\subsection{Methodology} 
\subsubsection{Setup}
For consistency, we simulated the same three censorship environments from 
our qualitative user study. Details of the mild, intermediate, and advanced 
censorship environments and what configurations are necessary for a 
successful connection can be found in Section \ref{sec:setup}.

@@

\begin{figure}
\centering
\includegraphics{time_to_success}
\caption{
Time to first success, by censorship environment and interface.
The dots show the raw completion times;
while the boxplots show the medians and interquartile ranges.
}
\end{figure}

@@

{\color {red} This will be the main part of the paper--where we report on the data that we collected through the xlab experiment. Some of the questions we want to answer are: did the new interface improve success rate? did the new interface only help certain people? Did people take longer or shorter in the new version? Did we shift participants' behaviors in the new interface? Are the way people approach trying different configurations affected? are there existing problems for both interfaces? (we know for sure that users still not receiving feedback is an issue. I don't know how many of our participants actually saw our helpful error messages, since they took minutes to pop up, and some never pop up at all..)}

\section{Future Work} 
{\color {red}
Wait to fill this section out until we have finished analyzing the data from the quantitative
user study experiment. A lot of the future work can be in reference to this. Or, we can even
talk about what is in the discussion section. ... OR, maybe this section isn't even necessary.\\

>>>>

\subsection{Methodology} 
In this section, we talk about the details of our qualitative user study, such as the censorship environments we placed our users in, how we pre-screened and selected our participants, and the procedure for the experiment.

\subsubsection{Setup}
\label{sec:setup}
We simulated three censorship environments for our experiment.
These reproducible, stable environments are informed by our experience 
with pluggable transports and knowledge of commonly seen censorship 
techniques. Their goal in our user study is not to replicate the network 
environment in any particular country, but to require our participants to 
configure Tor Browser in distinct configurations.

@@

\subsection{Results} 
In this section, we discuss problems encountered by our participants at each step of the configuration process and solutions to those problems. We conclude with our goals for improving the configuration interface. Because of the small sample size of qualitative studies, we can only state that these are problems that participants can encounter when configuring. We confirm the statistical significance of some of the problems in our quantitative study (section ~\ref {sec:quantitative}. All quotes are paraphrased from live transcriptions of participant interviews.\\

\subsubsection{Connect vs. Configure} 
The first task for our participants was to decide between connecting directly to the Tor network or configuring their connection. Text in the interface tells people that connecting directly ``will work in most situations'' and instructs to configure a bridge or proxy if the ``Internet connection is censored or proxied.'' We found that a majority of our participants did not take the time to read the text on the screen and that if they did, the text did not always soundly influence their decision.

@@

\subsubsection{Bridge Configuration} 
When a participant chooses to configure their connection, their next step is to determine whether they need to configure a bridge, and to configure one if necessary. Answering yes to ``Does your Internet Service Provider (ISP) block of otherwise censor connections to the Tor Network'' directs to a bridge configuration screen, whereas answering no skips that screen. We observed that multiple participants struggled with the technical language on the screen, and ultimately decided to try trial and error. Most participants with the default option to not configure a bridge.

@@

\subsubsection{Proxy Configuration} 
After the bridge configuration, the participant again is asked to answer a question to determine if they need a proxy and if so, to configure one. This question also was too technical for some participants.

@@

\subsubsection{Progress Bar} 
Users were generally displeased with the lack of feedback on the progress bar. The process seemed to take too long for them, even in the ideal case in which a user chose the correct configuration in the first attempt. If users chose particular wrong configurations (i.e. a syntactically valid but nonfunctional proxy), they would be waiting for an indefinite period of time, because there is no timeout.

@@

\subsubsection{User Communication} 
Many participants, including participants who were pre-screened for high technical ability and previous experience with using Tor, were not familiar with the vocabulary. 
\begin{quotation}
\noindent P2:\textit{"I don't know what any of those means (list of bridges),or what that (proxy)
 means at all."}\\

@@

@@

\section{Redesigning the Configuration Interface}
We believe that the interface is too technical for users to understand and overburdens users with tasks. From our observations in this qualitative study, our goal in redesigning the interface was to making the vocabulary more accessible to the average user, requiring the user to make fewer decisions, and automating parts of configuration that don't increase risk to high-risk users.

@@

Changes made:

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt 
\item Made first screen more clear to help users decide on connect vs configure. 
\item Got rid of question screens. 
\item Put the proxy first. It makes sense topologically. 
\item Added auto-detect for proxies. 
\item Gave explicit advice on how to choose bridges. 
\item Added a summary screen. 
\item Added a topological progress bar that works every time. 
\item Gives instructions on what to try next after failure. 
\item Greatly reduced text and made text easier to read. 
\item Less visual clutter for users. Hide things until user clicks on them. 
\end{itemize}

The design is a conservative design which accounts for at-risk users, backward compatibility, and maintainability.

@@

\subsection{Methodology} 
In this section, we talk about the details of our quantitative user study, such as the censorship environments we placed our users in, how we recruited our 124 participants, and the procedure for the experiment.

\subsubsection{Setup}
For consistency, we simulated the same three censorship environments from 
our qualitative user study. Details of the mild, intermediate, and advanced 
censorship environments and what configurations are necessary for a 
successful connection can be found in Section \ref{sec:setup}.

@@

\begin{figure}
\centering
\includegraphics{time_to_success}
\caption{
Time to first success, by censorship environment and interface.
The dots show the raw completion times;
while the boxplots show the medians and interquartile ranges.
The ``DNF'' figures at the right
show the number of participants who did not finish
in the time alloted.
}
\end{figure}

@@

{\color {red} 
What to talk about: 
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt 
\item{Did the new interface improve the success rate?}
\item{Did the new interface help in only certain environments or certain people?}
\item{Did the new interface improve the time to success?}
\item{What are remaining issues?} 
\item{What people did while configuring the interface}
\item{Where people downloaded Tor browser if they did it themselves} 
\item{Xlab versus craigslist} 
\end{itemize}

Graph: 
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt 
\item{success rate}
\item{time to success: distribution}
\item{time to success: cdf and cutoffs at 2 min, 10 min, 20 min?}  
\item{time spent on each screen}
\item{order pluggable transports were chosen}
\item{transitions between windows for all participants}
\end{itemize} 
}

\section{Future Work} 
{\color {red}
Wait to fill this section out until we have finished analyzing the data from the quantitative
user study experiment. OR, maybe this section isn't even necessary.\\
